Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-18 code/analysis.Rmd
cplot

c_over_phi <- cbind(rownames(coef(cmods))[2:4],coef(cmods)[2:4,]) %>%
  as.tibble() %>%
  mutate_all(as.numeric) %>%
  mutate(lab = "ESDL") %>%
  rename(phi = V1, C = V2)

fauria <- tibble(phi = c(.00817,.02163), C = c(3.18,1.53), lab = "Fauria")

@@

c_over_phi %>%
  ggplot(aes(x = phi, y = C, color = lab)) +
  geom_point() +
  theme_bw() +
  labs(title = "Comparison of power-law constant to Fauria et al. data",
       x = expression(phi))

lm(data = c_over_phi, formula = log10(C) ~ log10(phi)) %>% summary()

>>>>

c_over_phi <- cbind(rownames(coef(cmods))[2:4],coef(cmods)[2:4,]) %>%
  as.tibble() %>%
  mutate_all(as.numeric) %>%
  mutate(lab = "This study") %>%
  rename(phi = V1, C = V2)

fauria <- tibble(phi = c(.00817,.02163), C = c(3.18,1.53), lab = "Fauria et al. (2015)")

@@

lm(data = c_over_phi, formula = log10(C) ~ log10(phi)) %>%
  summary

c_phi_curve <- tibble(phi = seq(0.002,.03,by = .0001), C = 10^-2.0966*phi^-1.4107)

cplot <- c_over_phi %>%
  ggplot(aes(x = phi, y = C, color = factor(lab, levels = c("This study", "Fauria et al. (2015)")))) +
  geom_point(size = 2, pch = 4) +
  theme_bw() +
  labs(x = expression(phi[c]), color = "Study") +
  scale_color_manual(values = c("darkgreen","red")) +
  geom_line(data = c_phi_curve, aes(x = phi, y = C), inherit.aes = FALSE) +
  annotate("polygon", x=c(.012,.012,.004,.004,.007), y= c(23,27,27,23,23), color = "black", fill = "gray 97") +
  annotate("text", .008, 25, parse = TRUE, label = "C == 0.00801*phi^-1.41")

ggsave("../pics/cphiplot.png",cplot,dpi = 600)
